Projit: An Open Source tool for Decoupled Data Science

### 2024-09-29 docs/paper/paper.tex
Working on JOSS submission
Working on JOSS paper draft

@@

Frameworks for eScience will typically need to take a position on the extent to which 
they are domain specific versus general purpose. A domain specific approach can 
integrate multiple data sources in a domain aware fashion that can faciliate 
automated or assisted scientific discover\cite{Howe2008}. On the
other hand a general purpose framework facilitates multi-disciplinary collaboration 
and permits meta-analysis that transcends the boundaries of disciplines. 
The other key dimension for a decision is the extent to which an eScience 
application depends on specific technologies, many machine learning science platforms
can provide efficiency gains, but only when using specfic libraries and 
frameworks\cite{Alberti:2018,MolnerDomenech:2020}. Similarly, other empirical 
science platforms are built on specific database, webservers or application
frameworks, which make them less extensible and harder to integrate.

@@

\begin{figure*}
\includegraphics[scale=0.6]{./Projit_decoupled_process.drawio.png}
\caption{Projit Process for Decoupled Data Science}
\label{fig:projit}
\end{figure*}

>>>>

Software approaches to managing data, processes and meta-data are typically referred to 
as e-science platforms. In general they are either build for specific scientific domains
\cite{Howe2008,} or they are designed for very specific technology stacks (common in a given domain)
\cite{Subramanian2013}.

@@

Frameworks for eScience will typically need to take a position on the extent to which 
they are domain specific versus general purpose. A domain specific approach can 
integrate multiple data sources in a domain aware fashion that can faciliate 
automated or assisted scientific discovery\cite{Howe2008,Pettit:2010}. On the
other hand a general purpose framework facilitates multi-disciplinary collaboration 
and permits meta-analysis that transcends the boundaries of disciplines. 
The other key dimension for a decision is the extent to which an eScience 
application depends on specific technologies, many machine learning science platforms
can provide efficiency gains, but only when using specfic libraries and 
frameworks\cite{Alberti:2018,MolnerDomenech:2020}. Similarly, other empirical 
science platforms are built on specific database, webservers or application
frameworks, which make them less extensible and harder to integrate.

@@

\begin{figure*}
\includegraphics[scale=0.6]{./images/Projit_decoupled_process.drawio.png}
\caption{Projit Process for Decoupled Data Science}
\label{fig:projit}
\end{figure*}
